### 2024-06-16 basic-statistics.qmd
20240616 - table formatting

| Effect Size Index                             | Small        | Medium       | Large        |
|-----------------------------------------------|--------------|--------------|--------------|
| Cohen's d                                     | $\ge |.20|$ | $\ge |.50|$ | $\ge |.80|$ |
| Standardized regression coefficient ($\beta$) | $\ge |.10|$ | $\ge |.24|$ | $\ge |.37|$ |
| Correlation coefficient ($r$)                 | $\ge |.10|$ | $\ge |.24|$ | $\ge |.37|$ |
| Coefficient of determination ($R^2$)          | $\ge .01$   | $\ge .06$   | $\ge .14$   |
| Eta squared ($\eta^2$)                        | $\ge .01$   | $\ge .06$   | $\ge .14$   |
| Partial eta squared ($\eta_p^2$)              | $\ge .01$   | $\ge .06$   | $\ge .14$   |

>>>>

| Effect Size Index                             | Small       | Medium      | Large       |
|:----------------------------------------------|:------------|:------------|:------------|
| Cohen's d                                     | $\ge |.20|$ | $\ge |.50|$ | $\ge |.80|$ |
| Standardized regression coefficient ($\beta$) | $\ge |.10|$ | $\ge |.24|$ | $\ge |.37|$ |
| Correlation coefficient ($r$)                 | $\ge |.10|$ | $\ge |.24|$ | $\ge |.37|$ |
| Coefficient of determination ($R^2$)          | $\ge .01$   | $\ge .06$   | $\ge .14$   |
| Eta squared ($\eta^2$)                        | $\ge .01$   | $\ge .06$   | $\ge .14$   |
| Partial eta squared ($\eta_p^2$)              | $\ge .01$   | $\ge .06$   | $\ge .14$   |
